Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-06-26 man/figures/resilience_long_term.Rmd
update figure
add without 95

v = "rt"
x = 'd_severity'
formulita <- as.formula(paste0(v, "_mean_mean ~", x))

  eqns <- sdfsite %>% split(.$site) %>% 
    map(~ lm(formulita, data = .)) %>%
    map(lm_eqn) %>% 
    do.call(rbind, .) %>%
    as.data.frame() %>%
    set_names("equation") %>%
    mutate(site = rownames(.))

@@

```{r no95}
sdfsite95 <- df %>% 
  filter(samps >= 5) %>% 
  group_by(disturb_year, site) %>% 
  filter(disturb_year > 1940) %>% 
  filter(disturb_year != 1995) %>% 
  summarise_at(c("rt_mean", "rs_mean", "rc_mean", "rrs_mean"), 
               funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% 
  inner_join(dy, by=c("disturb_year" = "maxyear"))

@@

ggsave(filename = here::here("./man/figures/svg/fig_6_95.jpg"), 
       dpi = 300,  plot=res_long_term_sites95, width=9, height=7)

>>>>

@@

```{r no95}
sdfsite95 <- df %>% 
  filter(samps >= 10) %>% 
  group_by(disturb_year, site) %>% 
  filter(disturb_year > 1940) %>% 
  filter(disturb_year != 1995) %>% 
  summarise_at(c("rt_mean", "rs_mean", "rc_mean", "rrs_mean"), 
               funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% 
  inner_join(dy, by=c("disturb_year" = "maxyear"))

@@

ggsave(filename = here::here("./man/figures/svg/fig_6_95.jpg"), 
       dpi = 300,  plot=res_long_term_sites95, width=8.7, height=7)
